---
title: "Assignment 9"
author: "Max Hanscom"
date: "2023-01-30"
output:
  prettydoc::html_pretty:
    theme: architect
    highlight: github
---

**1.**
Using a for loop and an if statement, write a function to calculate the number of zeroes in a numeric vector. Before entering the loop, set up a vector of integers with some zero values. Then, set up a counter variable counter <- 0. Inside the loop, add 1 to counter each time you have a zero in the vector. Finally, use return(counter) for the output.
```{r}
my_vec <- c(1,0,2,0,3,4,5,0,6,0,8,9,0,10)
counter <- 0

for (i in 1:length(my_vec)) {
  if (my_vec[i] == 0) {
    counter <- counter + 1
  }
}
print(counter)
```

**2.**
Write a function that takes as input two integers representing the number of rows and columns in a matrix. The output is a matrix of these dimensions in which each element is the product of the row number x the column number.
```{r}
###################################
# FUNCTION: matrixMaker
# input: two integers
# output: matrix of dimention of integers, populated by row x col at each location

matrixMaker <- function(a=1, b=1){ 
  m <- matrix(1:(a*b), nrow=a)
  for(i in 1:nrow(m)){ 
    for(j in 1:ncol(m)){ 
      m[i,j] <- i * j
      }
    }  
  return(m)
  }
matrixMaker(8,8)

```

**3.**
Use a for loop to repeat your previous functions from Weekly Assignment 2 (which simulate a data frame and extract a p-value) 100 times. Store the results in a data frame that has 1 column indicating the replicate number and 1 column for the p-values (a total of 2 columns and 100 rows).
```{r}




```

